---
output:
  word_document: default
  html_document: default
---
# Module 6 - Assignment 1
## Farrell, Zach
### Clustering

```{r}
options(tidyverse.quiet=TRUE)
library(tidyverse)
library(cluster)
library(factoextra)
library(dendextend)
```

```{r}
trucks <- read_csv("trucks.csv")
```

```{r}
ggplot(trucks, aes(x = Distance, y = Speeding)) +
  geom_point()
```
There seems to be clustering around the 50 mile mark, and between the 100 and 200 mile mark.

```{r}
trucks2 = trucks %>% select(c("Distance","Speeding"))
trucks2 = scale(trucks2)
as.data.frame(trucks2)
```

```{r}
set.seed(1234)
clusters1 <- kmeans(trucks2, 2)
```

```{r}
fviz_cluster(clusters1, trucks2)
```

```{r}
set.seed(123)
fviz_nbclust(trucks2, kmeans, method = "wss")
```
4 is the optimal amount of clusters according to the wss method

```{r}
set.seed(123)
fviz_nbclust(trucks2, kmeans, method = "silhouette")
```
4 is the optimal amount of clusters according to the silhouette method. the two methods are at a consensus.

```{r}
set.seed(1234)
clusters2 <- kmeans(trucks2, 4)
```

```{r}
fviz_cluster(clusters2, trucks2)
```
Cluster 1 includes people who are speeding at a higher degree of standard deviation than the average.  Cluster 2 includes people who dont speed as much, even if they are driving a long way.  Cluster 3 includes people who dont speed as much because they have shorter trips.  And finally Cluster 4 includes people who sometimes speed on long trips.

```{r}
wine <- read_csv("wineprice.csv")
```

```{r}
wine2 = wine %>% select(c("Price","WinterRain","AGST","HarvestRain","Age"))
wine2 = scale(wine2)
as.data.frame(wine2)
```

```{r}
set.seed(123)
fviz_nbclust(wine2, kmeans, method = "wss")
```

```{r}
set.seed(123)
fviz_nbclust(wine2, kmeans, method = "silhouette")
```
It looks to me to be 4 or 5 based on the wss method, and it is 5 usint the silouette method.  so the consensus will be 5

```{r}
set.seed(1234)
clusters3 <- kmeans(wine2, 5)
```

```{r}
fviz_cluster(clusters3, wine2)
```

```{r}
m = c( "average", "single", "complete", "ward")
names(m) = c( "average", "single", "complete", "ward")

ac = function(x) {
  agnes(wine2, method = x)$ac
}
map_dbl(m, ac)
```

```{r}
hc = agnes(wine2, method = "ward") 
pltree(hc, cex = 0.6, hang = -1, main = "Agglomerative Dendrogram") 
```

```{r}
hc2 = diana(wine2)
pltree(hc2, cex = 0.6, hang = -1, main = "Divisive Dendogram")
```

```{r}
plot(hc2, cex.axis= 0.5) 
rect.hclust(hc2, k = 5, border = 2:6)
```
















